Parsing Tweets into Universal Dependencies

### 2017-11-13 paper.tex
mention 280 char limit, minor change in abstract

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}

@@

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank which has 55,607 tokens and it's more than 4 times
larger than the {\sc Tweebank v1}. We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
\end{abstract}

@@

The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic function.
In our annotation, there are five types of non-syntactic tokens: 
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.

>>>>

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
\newcommand{\yicomment}[1]{\textcolor{red}{[#1 ---\textsc{nas}]}}

@@

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachements. 
It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
\end{abstract}

@@

The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic function.
In our annotation, there are five types of non-syntactic tokens: 
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words \footnote{Tweets we analyze have 140 character limits. Although Twitter has now doubled the tweet limit to 280 characters, we believe this type of tokens will still remain.}. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}\footnote{The statistics are obtained on 140 character limit tweets.}.
